Corotating Clumps Around Adolescent Low-Mass Stars: Four Years of TESS

### 2023-07-07 paper/ms.tex
update ms

\begin{figure*}[!t]
	\begin{center}
		\centering
		\includegraphics[width=\textwidth]{f6.pdf}
		\vspace{-0.45cm}
		\caption{
      {\bf Properties of CQVs from our serach}.
      The \ngoods\ bonafide CQVs in Table~\ref{tab:thetable} are 
      the black circles; \nmaybes\ candidate CQVs are gray circles.
      The \nstarssearched\ target stars with 120-second cadence data
      acquired by TESS between July~2018 and Sep~2022 are shown as the shaded background on the top panels,
      where darker regions correspond to a larger relative number of observed stars.
      {\bf lgb todo: P vs color needs Pleiades comparison}
		}
		\label{fig:catalogscatter}
	\end{center}
\end{figure*}

@@

It is amusing that in identifying the two candidate CQV sources in
Section~\ref{subsec:irexcess} with outlying SEDs (TICs~193136669 and
TIC~57830249), we were prompted to reconsider our light curve-based
labeling, to
ultimately conclude that these sources are dippers.  This episode
suggests that could be some overlap between the two classes of
object.  It is also worth emphasizing that our labeling of
e.g.~TIC~57830249 was based on a single sector of TESS data
(Sector~36) when its behavior is relatively periodic and it showed
relative dip depths of a few percent.  However in other TESS sectors
(e.g. Sector~10), this source looks completely different, varying in
apparent flux by a factor of two, with hardly any discernible
periodicity at all.

Comparing these results against the backdrop of our increasing
understanding of dippers
\citep[e.g.][]{2014AJ....147...82C,2016ApJ...816...69A,2021ApJ...908...16R,2022ApJS..263...14C},
it is clear that the loss of an infrared excess is associated with
strong changes in a star's optical variability.  It is reasonable to
imagine connections between CQVs and dippers: both classes of object
can show transient flux dips that are relatively narrow in duration.
Such dips in both are probably associated with clumps of dust or gas.
However the CQV dips are typically {\it i)} more periodic and {\it
ii)} less deep than those of dippers, and {\it iii}) they display far
less transience over timescales of a few to tens of cycles.  This is
probably because CQV stars have demonstrably less dust than (most)
dipper stars.  At a population level, the CQV stars are also older.  A
common mystery between the CQVs and dippers, in our own estimation, is
how exactly the {\it narrowness} of the dust clumps is produced.  It
is not unreasonable to imagine a similar mechanism operating for both
types of object, tied perhaps to a shared magnetic topology, or
perhaps to a preference for dust to inspiral to the star in clumped
structures.

@@

We can estimate the mass of a transiting cloud by first converting the
transit depth to an effective cloud radius, $R_{\rm cloud}$.  For most
CQVs in Figure~\ref{fig:cqvs}, this typically yields $\approx$2-20\,$R_\oplus$.
This size can be converted into a mass estimate by requiring the
optical depth $\tau$ of the cloud to be at least unity and by positing
some composition for the cloud.  In other
words, a minimum constraint on the number density follows by
requiring the cloud to be optically thick.  For cases like LP 12-502,
this is resonable because the transit duration implies $R_{\rm
cloud}\ll R_\star$.  Carrying out the relevant calculation assuming
a dust composition, for dust grains 1\,$\mu$m in size,
\citet{2023MNRAS.518.4734S} find minimum cloud masses of order
$10^{12}$\,kg (their Eq.~23), which scale linearly with both the
optical depth and dust grain radius.  This is roughly comparable to a
small asteroid; the asteroid belt itself has a mass of
order $\approx$10$^{21}$\,kg (CITE).  Also by way of comparison,
the previously-discussed cool gas prominences for AB~Dor would need to
have masses of order $10^{14}$\,kg \citep{1990MNRAS.247..415C}, about
100$\times$ larger than the requisite dust mass.

>>>>

\begin{figure*}[!t]
	\begin{center}
		\centering
		\includegraphics[width=\textwidth]{f6.pdf}
		\vspace{-0.45cm}
		\caption{
      {\bf Properties of CQVs from our search}.
      The \ngoods\ bonafide CQVs in Table~\ref{tab:thetable} are 
      the black circles; \nmaybes\ candidate CQVs are gray circles.
      The \nstarssearched\ target stars with 120-second cadence data
      acquired by TESS between July~2018 and Sep~2022 are shown as the shaded background on the top panels,
      where darker regions correspond to a larger relative number of observed stars.
      {\bf lgb todo: P vs color needs Pleiades comparison}
		}
		\label{fig:catalogscatter}
	\end{center}
\end{figure*}

@@

It is amusing that in identifying the two candidate CQV sources in
Section~\ref{subsec:irexcess} with outlying SEDs (TICs~193136669 and
TIC~57830249), we were prompted to reconsider our light curve-based
labeling, to
ultimately conclude that these sources are dippers.  This episode
suggests that there could be overlap between the two classes of
object.  It is also worth emphasizing that our labeling of
e.g.~TIC~57830249 was based on a single sector of TESS data
(Sector~36) when its behavior is relatively periodic and it showed
relative dip depths of a few percent.  However in other TESS sectors
(e.g. Sector~10), this source looks completely different, varying in
apparent flux by a factor of two, with hardly any discernible
periodicity at all.

Comparing these results against the backdrop of our increasing
understanding of dippers
\citep[e.g.][]{2014AJ....147...82C,2016ApJ...816...69A,2021ApJ...908...16R,2022ApJS..263...14C},
it is clear that the loss of an infrared excess is associated with
strong changes in a star's optical variability.  It is reasonable to
imagine connections between CQVs and dippers: both classes of object
can show transient flux dips that are relatively narrow in duration.
The dips in both are probably associated with clumps of dust or gas.
However the CQV dips are typically more periodic and 
less deep than those of dippers, and they display far
less transience over timescales of a few to tens of cycles.  This is
probably because CQV stars have demonstrably less dust than (most)
dipper stars.  At a population level, the CQV stars are also older.  A
common mystery between the CQVs and dippers, in our own estimation, is
how exactly the {\it narrowness} of the dust clumps is produced.  It
is not unreasonable to imagine a similar mechanism operating for both
types of object, tied perhaps to a shared magnetic topology, or
perhaps to a preference for dust to inspiral to the star in clumped
structures.

@@

We can estimate the mass of a transiting cloud by first converting the
transit depth to an effective cloud radius, $R_{\rm cloud}$.  For most
CQVs in Figure~\ref{fig:cqvs}, this typically yields $\approx$2-20\,$R_\oplus$.
This size can be converted into a mass estimate by requiring the
optical depth $\tau$ of the cloud to be at least unity and by positing
some composition for the cloud.  In other
words, a minimum constraint on the number density follows by
requiring the cloud to be optically thick.  For cases like LP 12-502,
this is resonable because the transit duration implies $R_{\rm
cloud}\ll R_\star$.  Carrying out the relevant calculation assuming
the occulting material is dust grains 1\,$\mu$m in size,
\citet{2023MNRAS.518.4734S} find minimum cloud masses of order
$10^{12}$\,kg (their Eq.~23), which scale linearly with both the
optical depth and dust grain radius.  This is roughly comparable to a
small asteroid; the asteroid belt itself has a mass of
order $\approx$10$^{21}$\,kg (CITE).  Also by way of comparison,
the previously-discussed cool gas prominences for AB~Dor would need to
have masses of order $10^{14}$\,kg \citep{1990MNRAS.247..415C}, about
100$\times$ larger than the requisite dust mass.
